---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(knitr)
library(tidyverse)
library(gridExtra)
library(loamr)
set.seed(1)
```

# loamr: limits of agreement with the mean
`loamr` is an `R` package for performing agreement analysis on continuous measurements made by multiple observers on a number of subjects. The package provides functions for making agreement plots and for calculating the estimate and CI for the limits of agreement with the mean proposed by Christensen et al. (2020). 


## Installation
`loamr` can be installed using the following command:
```{r, eval = FALSE}
devtools::install_github("HaemAalborg/loamr")
```

## Example
The package includes a function to simulate data from the two-way random effects model
described in Christensen et al (2020):

```{r}
sim <- simMD(subjects=80, observers=10)
head(sim)
```
Estimate and CI for the limits of agreements with the mean:
```{r}
LOAM(sim)
```

The S3 class includes a generic plotting function made with `ggplot2` for making an 
agreement plot with indication of estimate and CI for the limits of agreement with the mean:
```{r}
plot(LOAM(sim))
```

Elements of the plot can be easily changed, e.g. the title:
```{r fig.height=4, fig.width=10}
plot(LOAM(sim)) + labs(title="Simulated Data")
```


## References

1. Christensen, H. S., Borgbjerg, J., Børty, L., and Bøgsted, M. (2020) 
"On Jones et al.'s method for extending Bland-Altman plots to limits of agreement with the mean for 
multiple observers". BMC Medical Research Methodology. https://doi.org/10.1186/s12874-020-01182-w











