---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(knitr)
library(tidyverse)
set.seed(1)
```

# loamr
loamr is an R package to ...



## Installation
loamr may be installed using the following command
```{r, eval = FALSE}
devtools::install_github("HaemAalborg/loamr")
```

# Overview
The package includes some data from Jones, this is in wide format, so we transform this to a long format as the 'LOAM' function uses:

```{r}
library(loamr)
data(Jones)
head(Jones)

Jones <- Jones %>%
  mutate(subject = 1:nrow(.)) %>%
  gather(reader, value, -subject)
```

Ww can calculate the Limit of Agreements and confidence intervals

```{r}
LOAM(Jones)
```

The S3 class includes a generic plotting function made with ggplot2

```{r fig.height=4, fig.width=10}
plot(LOAM(Jones))
```

## Simulation of Data
The package also includes a function to simulate data (which is already in long format)

```{r}
sim <- simMD(subjects=80, readers=4)
LOAM(sim)
```

We can plot this, and as the plotting is done by ggplot2 it's easy to change elements of the plot, like the title:

```{r fig.height=4, fig.width=10}
plot(LOAM(sim), CI="asym") + labs(title="Simulated Data")
```


## References

1. Jones'
2. Borgbjerg's