---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(knitr)
library(tidyverse)
library(gridExtra)
library(loamr)
set.seed(1)
```

# loamr
loamr is an R package for performing an agreement analysis for continuous measurements by multiple observers as suggested by Christensen et al. Specifically, the package can be used for making agreement plots and calculation of the estimate and CI for the limits of agreement with the mean proposed by Christensen et al. 


## Installation
loamr may be installed using the following command
```{r, eval = FALSE}
devtools::install_github("HaemAalborg/loamr")
```

# Overview

## Simulation of Data
The package includes a function to simulate data from the two-way random effects model:

```{r}
sim <- simMD(subjects=80, observers=10)
LOAM(sim)
```

The S3 class includes a generic plotting function made with ggplot2.
As the plotting is done by ggplot2 it's easy to change elements of the plot, like the title:

```{r fig.height=4, fig.width=10}
plot(LOAM(sim), CItype="asym") + labs(title="Simulated Data")
```


## References

1. Christensen et al.











