---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(knitr)
library(loamr)
set.seed(1)
```

# loamr: limits of agreement with the mean

loamr` is an `R` package for performing agreement analysis on continuous
measurements made by multiple observers. The package provides functions for

* making agreement plots and calculating the estimate and CI for the limits of
  agreement with the mean (LOAM) proposed by Christensen et al. (2020),
* the extension in Christensen et al. (2025) to repeated measurements, which
  allows a *repeatability* LOAM to be calculated in addition to the
  *reproducibility* LOAM, and optionally includes a subject-observer
  interaction in the model, and
* comparing the LOAMs obtained from two measurement methods applied to the same
  subjects and observers, using a parametric bootstrap.

## Installation
`loamr` can be installed using the following command:
```{r, eval = FALSE}
devtools::install_github("CLINDA-AAU/loamr")
```

## Example: one measurement per subject and observer

The package includes a function to simulate data from the two-way random effects
model described in Christensen et al. (2020), as well as from the extended model
with a subject-observer interaction term described in Christensen et al. (2025):

```{r}
sim <- simMD(mu = 5)
head(sim)
```

Estimate and CI for the limits of agreements with the mean:

```{r}
LOAM(sim)
```

The S3 class includes a generic plotting function made with `ggplot2` for making an 
agreement plot with indication of estimate and CI for the limits of agreement with the mean:

```{r}
plot(LOAM(sim))
```

Elements of the plot is easily changed using functionalities from `ggplot2`. For 
example, changing the title:

```{r fig.height=4, fig.width=10}
plot(LOAM(sim)) + ggplot2::labs(title = "Simulated Data")
```

## Example: repeated measurements and interaction

The **reproducibility LOAM** can always be calculated, also when there is only one
measurement per subject and observer. When each observer measures each subject
more than once, a **repeatability LOAM** can be calculated as well (Christensen et al. 2025):

* The **reproducibility LOAM** reflects all sources of variation between
  measurements on the same subject: differences between observers (and, if
  included, the subject-observer interaction) as well as variation between
  repeated measurements.
* The **repeatability LOAM** only reflects variation between repeated
  measurements by the *same* observer on the same subject.

```{r}
sim_rep <- simMD(mu = 5, sigma2AB = 0.3, interaction = TRUE,
                 n_subjects = 20, n_observers = 8, n_measurements = 3)
head(sim_rep)
```

```{r}
fit <- LOAM(sim_rep, interaction = TRUE)
fit$estimates
fit$intervals
```

Once there is more than one measurement per subject-observer combination, both
LOAMs are reported. With a single measurement per combination, only the
reproducibility LOAM is available.


## Example: comparing two measurement methods

`LOAM_diff_boot()` compares the LOAMs from two methods (for example CT and MRI)
applied to the same subjects by the same observers, with the same number of
repeated measurements. It returns a confidence interval for the difference
between the two LOAMs and a p-value for testing that they are equal, for
reproducibility and, when there are repeated measurements, also for
repeatability. Since the two LOAM estimates are dependent, a parametric bootstrap
based on a bivariate two-way random effects model is used.

`data1` and `data2` must be in the same long format as for `LOAM()`, with the same
subject/observer/measurement combinations. Here they are simulated independently,
so there is no correlation between the methods; this is for illustration only.

```{r}
method1 <- simMD(mu = 5, sigma2B = 1,   n_subjects = 20, n_observers = 8, n_measurements = 3)
method2 <- simMD(mu = 5, sigma2B = 2.5, n_subjects = 20, n_observers = 8, n_measurements = 3)

res <- LOAM_diff_boot(method1, method2, R = 500, seed = 1)
res
```

The `interaction` argument works as for `LOAM()`, and one-sided tests are available
through `alternative = "less"` or `alternative = "greater"`.

A larger `R` gives more stable results; `R = 500` is used here to keep the
example fast. The constructed confidence interval is a basic bootstrap interval.

## References

1. Christensen, H. S., Borgbjerg, J., Børty, L., and Bøgsted, M. (2020) 
"On Jones et al.'s method for extending Bland-Altman plots to limits of agreement with the mean for 
multiple observers". BMC Medical Research Methodology. https://doi.org/10.1186/s12874-020-01182-w

2. Christensen, H. S., Bøgsted, M., and Borgbjerg, J. (2025) 
"A statistical note on extending Christensen's limits of agreement with the mean". 
ArXiv (preprint). https://doi.org/10.48550/arXiv.2508.16250








