---
title: "Limits of agreement with the mean (LOAM) for Woo et al."
output:
  word_document: 
    fig_caption: yes

references:
- id: woo2020
  title: Retrospective comparison of approaches to evaluating inter-observer variability in CT tumour measurements in an academic health centre
  author:
  - family: Woo
    given: MinJae
  - family: Heo
    given: Moonseong
  - family: Devane
    given: A Michael
  - family: Lowe
    given: Steven C
  - family: Gimbel
    given: Ronald W
  container-title: Nature Materials
  volume: 11
  issue: 4
  type: article-journal
  issued:
    year: 2012
    
- id: christensen
  title: On Jones et al.'s method for extending Bland-Altman plots to limits of agreement with the mean for multiple observers
  author:
  - family: Christensen
    given: Heidi S
  - family: Borgbjerg
    given: Jens
  - family: Børty
    given: Lars
  - family: Bøgsted
    given: Martin
  container-title: BMC Medical Research Methodology
  volume: 20
  issue: 1
  type: article-journal
  issued:
    year: 2020
---


```{r include=FALSE}
library(knitr)
library(loamr)
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(echo = FALSE)
```

```{r}
obs <- read.csv("data/observed.csv",  header = F)
inc <- read.csv("data/increased.csv", header = F)
dec <- read.csv("data/decreased.csv", header = F)

df.obs <- obs %>% 
  mutate(subject = 1:nrow(.)) %>% 
  gather(observer, value, -subject) %>% 
  mutate(observer = as.numeric(sub(".", "", observer)))

df.inc <- inc %>% 
  mutate(subject = 1:nrow(.)) %>% 
  gather(observer, value, -subject) %>% 
  mutate(observer = as.numeric(sub(".", "", observer)))

df.dec <- dec %>% 
  mutate(subject = 1:nrow(.)) %>% 
  gather(observer, value, -subject) %>% 
  mutate(observer = as.numeric(sub(".", "", observer)))

df.all <- bind_rows(list(Observed  = df.obs, 
                         Decreased = df.dec, 
                         Increased = df.inc), .id = "df") %>% 
  mutate(df = factor(df, levels = c("Decreased", "Observed", "Increased")))
```


Woo et al. have provided an open access dataset based on the diameters of 10 CT 
metastatic lesions measured by 13 observers [@woo2020]. This dataset was 
supplemented by two additional datasets where increased and decreased measurement 
variability was simulated from the aforementioned dataset. For each of these three
datasets, agreement plots as well as estimates and 
for the 95% limits of agreement with the mean (LOAM) and the subject, observer, 
and residual standard deviation components from the underlying two-way random 
model [see @christensen] can be found in the following.

## The three datasets
```{r, fig.width = 7.5, fig.height = 5.5, fig.cap = "\\label{fig:data}Plot of the measurements from each of the three datasets."}
df.all %>% 
  ggplot(aes(factor(subject), value, color = df)) +
  geom_jitter(position = position_dodge(0.5)) +
  labs(color = "Dataset", x = "CT image set", y = "Measurement") +
  theme_bw() + theme(panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank())
```

&nbsp;

## Agreement plots
```{r, fig.width = 8, fig.height=4, fig.cap = "\\label{fig:agreeplot}Agreement plots with estimates (dashed line) and 95% CIs (shaded regions) for the 95% LOAM from @christensen."}
plot(LOAM(df.dec)) + 
    scale_y_continuous(limits = c(-1.4, 1.4)) +
    labs(title = NULL, subtitle = "Decreased") +
    theme(plot.subtitle = element_text(hjust = 0.5)) +
  plot(LOAM(df.obs)) + 
    scale_y_continuous(limits = c(-1.4, 1.4)) +
    labs(title = NULL, subtitle = "Observed") +
    theme(plot.subtitle = element_text(hjust = 0.5)) +
  plot(LOAM(df.inc)) + 
    scale_y_continuous(limits = c(-1.4, 1.4)) +
    labs(title = NULL, subtitle = "Increased") +
    theme(plot.subtitle = element_text(hjust = 0.5)) 
```

&nbsp;

## Estimates and CIs 

```{r}
LOAM.dec <- LOAM(df.dec)

est <- lapply(c("Decreased", "Observed", "Increased"), 
       function(x){
         res <- LOAM(df.all %>% filter(df == !!x))
         out <- paste0(round(res$estimates, 2), 
                       " (", round(res$intervals[1, ], 2), 
                       ", ", round(res$intervals[2, ], 2), ")")
         out <- data.frame(x, t(out))
         colnames(out) <- c("Data", colnames(res$estimates))
         subset(out, select = -ICC)
}); est <- do.call(rbind, est)

colnames(est) <- c("Dataset", "LOAM (CI)", "$\\hat\\sigma_A$ (CI)", "$\\hat\\sigma_B$ (CI)",
                   "$\\hat\\sigma_E (CI)$")
kable(est, escape = F, caption = "Estimates and 95% CIs for the upper 95% LOAM and 
the standard deviation components for subject, observer and residual variation ($\\sigma_A$, $\\sigma_B$, and $\\sigma_E$, respectively) 
from the two-way random model in @christensen.")
```

# References